Age-related changes in plant growth and traits

### 2015-03-31 leaflifespan.Rmd
creating separate R scripts for analysis of different variables

#discuss with Daniel
- once we are certain about leaf lifespan calculations, those calculations should go into a separate file, since that is background processing, but like calculating investment. Then this becomes the file where variables are summarized, plotted analyzed.
- add final leaf and stem biomass output to "investment" output file
- seed weight vs. propagule weight dilemma

@@

@@

#adding variables to look at change across years
SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
SummaryInd$change_basal_diam <- SummaryInd$FinalBasalDiam - SummaryInd$StartBasalDiam
SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((SummaryInd$d_start/2)^2))
SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
```

@@

#leaf lifespan summary by species, age
LL_summary <- SummaryInd %>%
  filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area)

@@

@@

#merge various data summaries into SummarySppAge dataframe
SummarySppAge <- merge(LL_summary, LMA_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, wood_summary, by=c("species"))
SummarySppAge <- merge(SummarySppAge, seedsize, by=c("species"))
SummarySppAge <- merge(SummarySppAge, maxH_spp, by=c("species"))
SummarySppAge <- merge(SummarySppAge, maxH, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, investment_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))

@@

>>>>

#discuss with Daniel
- once we are certain about leaf lifespan calculations, those calculations should go into a separate file, since that is background processing, but like calculating investment. Then this becomes the file where variables are summarized, plotted analyzed.
-Similarly, have separate file where all teh summary calculations occur
- add final leaf and stem biomass output to "investment" output file
- seed weight vs. propagule weight dilemma

@@

#calculating percentages of various accessory tissues

accessory$PerPrePol_A <- accessory$PrePol_A / accessory$Total
accessory$PerPrePol_S <- accessory$PrePol_S / accessory$Total
accessory$PerPostPol_A <- accessory$PostPol_A / accessory$Total
accessory$PerPackDisp <- accessory$PD / accessory$Total
accessory$PerPropagule <- accessory$Prop / accessory$Total
accessory$PerAcc <- 1- accessory$PerPropagule

accessory$PerPrePol_A[which(is.nan(accessory$PerPrePol_A))] <- NA
accessory$PerPrePol_S[which(is.nan(accessory$PerPrePol_S))] <- NA
accessory$PerPostPol_A[which(is.nan(accessory$PerPostPol_A))] <- NA
accessory$PerPackDisp[which(is.nan(accessory$PerPackDisp))] <- NA
accessory$PerPropagule[which(is.nan(accessory$PerPropagule))] <- NA
accessory$PerAcc[which(is.nan(accessory$PerAcc))] <- NA

@@

#adding variables to look at change across years, RGR
SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
SummaryInd$change_basal_diam <- SummaryInd$FinalBasalDiam - SummaryInd$StartBasalDiam
SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((SummaryInd$d_start/2)^2))
SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
SummaryInd$RGR <- log(SummaryInd$FinalWeight)-log(SummaryInd$FinalWeight-SummaryInd$GrowthInv)
```

@@

#leaf lifespan summary by species, age
LL_summary <- SummaryInd %>%
  filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area,RGR)

@@

accessory_summary2 <- accessory %>%
  filter(Total!=0) %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), PerPrePol_A, PerPrePol_S, PerPostPol_A, PerPackDisp, PerPropagule, PerAcc)

@@

#merge various data summaries into SummarySppAge dataframe
SummarySppAge <- merge(LL_summary, LMA_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, wood_summary, by=c("species"))
SummarySppAge <- merge(SummarySppAge, seedsize, by=c("species"))
SummarySppAge <- merge(SummarySppAge, maxH_spp, by=c("species"))
SummarySppAge <- merge(SummarySppAge, maxH, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, investment_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, accessory_summary2, by=c("species","age"))
SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))

@@

#Plots indicating there is a fundamental problem with leaf lifespan measurements
```{r, echo=FALSE,results='hide', message=FALSE}
plot(LL_death ~ LL_birth, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
mod <- lm(LL_death ~ LL_birth, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4&LL_birth!=Inf))
summary(mod)

plot(LL_death ~ LL_bd, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
mod <- lm(LL_death ~ LL_bd, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
summary(mod)
```
